### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to prelude sub-section

\section{Prelude}
\label{sec: overview}
%what do we have inside galaxies:
% stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, black holes, and high amount of dust and gas which all affect each others' formation, evolution and extinction.
There are also dark matter inside every galaxy, which to the best our knowledge only has gravitational effect on the galaxies.
All the information we can obtain from galaxies other than our owns are implanted in their light. % now we can detect gravitational wave which is not part of the SEDs, right?
Light emitted from young and evolved stars, and dust and gas in the space between stars have the most contribution on spectral energy distributions (SEDs) of galaxies.
We cannot detect any contribution from planets and black holes on SEDs due to their low intensity or the limitation of our detectors.
Therefore, with properly modeling observed features in SEDs we can extract information about evolution of stars, dust and gas inside galaxies.

%stars
Arguably, stars are the main component of normal galaxies.
They control the chemical composition and structure of galaxies by transforming gas into new born stars and by transforming death stars to the gas.
They are also central to the formation and evolution of planetary systems.
The energy provided by stars is necessary to create and maintain the life on planets. 
The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System.
Furthermore, in order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary. 
As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.

%ISM 1)Gas 2)dust
There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas.
Gas and dust in galaxies can be found in the space between stars that is called interstellar medium (ISM) which is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
Effect of ISM in stellar formation is undeniable; ISM provides raw material for formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying ISM is not only essential for understanding of the formation of stars but also it is necessary for interpretation of stellar evolution in that stars release their material into ISM when they reach at the end of their evolution.

% Metallicity
Metallicity, which is defined as the ratio of abundance of metal to the abundance of hydrogen atom, affects formation and evolution of stars indisputably.
In a galaxy like our own, star formation begins with condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in ISM which is due to gravitational instabilities. 
The interplay of turbulence and magnetic field with self-gravity is believed to be responsible for the formation of clumps within GMCs. 
Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution (see~\cite{McKee07} for more detail).
\cite{Walch11} showed that in case of the large scale turbulence the amount of metallicity on star formation is negligible, but if turbulence is decaying  metallicity has high impact and stabilizing self-gravitating cores.
Metals also play an important role on heating, cooling and ionizing processes in ISM. %%ADD ref.
Since cooling is one of the main reason of condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. %Sahar: should I talk about metallicity in stars and their relation with age?

%what does SED look like?
Our primary source of information for galaxies, specifically unresolved ones, is their SEDs.
Broadly speaking, young and hot stars emit most of their light in Ultraviolet (UV) wavelengths, evolved stellar population show themselves in optical and near-Infrared (NIR) emission and gas and dust heated by stellar emission are bright in Mid-IR (MIR) or far-IR (FIR) wavelengths.
Therefore, UV-to-IR SEDs contains valuable information about stellar evolution and their ISM. 
Other wavelengths regimes in SEDs (i.e. X-ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shock, are beyond the scope of this thesis.
general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rate (SFR), emit bulk of their energy in UV, while light of quiescent galaxies are dominated by optical and IR emission 
Detail information about age of stellar populations and other properties of galaxies can be determine by properly modelling of galaxy SEDs.

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass
Stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, is widely utilized from 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grains emission such as polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}, to fit the observed SEDs.
Many groups modelled SEDs for different type of galaxies and created templates of SEDs. (for more information see review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs using the templates.
Code Investigating GALaxy Emission ({\em CIGALE})~\citep{Noll09} is one example of codes that find best SED fittings.
It combines some of the SED models to find best SED fitting for given observed data in the rest-frame of UV-to-IR and find physical properties of galaxies such as SFR, Stellar mass and dust attenuation.

In this chapter, we present a review of observational method of measuring the star formation rate and the main properties that affect measuring and scaling the SFR. A discussion of the ISM, its role on star formation is presented in $\S$~\ref{sec: ism_intro}, In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}. The current issues about studying star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.

>>>>

\section{Prelude}
\label{sec: overview}
%what do we have inside galaxies:
% stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas, which all affect each others' formation, evolution and extinction.
There is also dark matter inside every galaxy, which to the best of our knowledge only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light. % now we can detect gravitational wave which is not part of the SEDs, right? % PB: right.
Young and evolved stars and dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies. %PB: explain what you mean by spectral energy distribution
We cannot detect any contribution from planets and black holes to SEDs due to their low intensity compared to these other components. %or the limitation of our detectors. % PB: need to rephase a bit  to mention AGN!
Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.

%stars
Arguably, stars are the main component of normal galaxies.
They control the chemical composition and structure of galaxies by transforming gas into new stars and by transforming dead stars back into gas.
They are also central to the formation and evolution of planetary systems.
The energy provided by stars is necessary to create and maintain the life on planets. 
The study of the formation and evolution of the Sun, and more generally that of stars, helps us understand more about our origin and the future of our Solar System.
Furthermore, in order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary. 
As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.

%ISM 1)Gas 2)dust
There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas. %PB: this is a very strong statement. Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now). So qualify this a bit.
Gas and dust in galaxies can be found in the space between stars that is called the interstellar medium (ISM). The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
The effect of the ISM on stellar formation is undeniable;  it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution in that stars release their material into the ISM when they reach the end of their evolution.

% Metallicity %PB: you start talking about metallicity but then switch over to SF. Overview the SF process first, then talk about how metallicity affects it.
Metallicity, which is defined as the ratio of abundance of metals to the abundance of hydrogen, affects formation and evolution of stars indisputably. %PB: define what "metals" means here
In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the ISM due to gravitational instabilities. 
The interplay of turbulence and magnetic fields with self-gravity is believed to be responsible for the formation of clumps within GMCs. 
Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic fields play central roles in defining this distribution (see~\cite{McKee07} for more detail). %PB: this sentence has a lot of concepts in it: going to be hard for non-astronomer to understand
\cite{Walch11} showed that in the case of large scale turbulence, the effect of metallicity on star formation is negligible, but if turbulence is decaying,  metallicity has a strong impact on stabilizing self-gravitating cores. %PB: please check edits to prev sentence
Metals also play an important role in heating, cooling and ionizing processes in the ISM. %%ADD ref.
Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. %Sahar: should I talk about metallicity in stars and their relation with age? %PB: yes. Need to introduce the general idea of chemical evolution - you hint at this above, but can state it explicitly.

%what does SED look like?
Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. %PB: since SED is a really important concept, I took out the acronym here.
Broadly speaking, young and hot stars emit most of their light in iltraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
Therefore, UV-to-IR SEDs contain valuable information about galaxies' stellar evolution and their ISM. 
Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
The general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission. 
Detailed information about the age of stellar populations and other properties of galaxies can be determined by modelling their SEDs.

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass %PB: Need more detail here - how do SED models include SFR, Mstar, etc?
The stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.%, to fit the observed SEDs.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models to find the best-fit SED for observed data in the rest-frame UV-to-IR and finds physical properties of galaxies such as SFR, stellar mass and dust attenuation.

%PB: I think you need a one-or-two sentence intro to the overall thesis goals here, so that the reader can see why you are talking about all of this stuff.
In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR. A discussion of the ISM and its role in star formation is presented in $\S$~\ref{sec: ism_intro}. In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}. Current issues about star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.
